Cosmic web alignments with the shape, angular momentum and peculiar velocities of dark matter halos

### 2014-05-08 paper/main.tex
new references

There is a long observational tradition studying galactic properties
as a function of their large scale environment
\citep[e.g.][]{Oemler1974,Dressler1980,Pimbblet2002,Gomez2003,Kauffmann2004,Abbas2006,Baldry2006,Park2007,OMill2008,Gonzalez2009,Padilla2010,Wilman2010,Muldrew2012}. In
these situations the environment definition is usually based on
quantities easily accessible to observations such as local number
density or nearest neighbour measurements. With
the advent of large surveys the visibility of the cosmic web became
clear. As a consequence, in order to capture its filamentarity, the
environment definition started to be more complex, involving shear and gradient properties of the galaxy density field or the reconstructed dark
matter density/velocity field
\citep[e.g.][]{Lee2005,AragonCalvo2007,Hahn2007,Sousbie2008,Zhang2009,Tweb,MunozCuartas2011,Vweb,Trowland2013,Tempel2014}.

@@

We caution the reader that the results reported by
\citep{Vweb, Libeskind2013,Wang2013} use a velocity field that is
calculated by a gaussian smoothing of the CIC velocity field without
taking into account any weight by mass.

@@

A much weaker alignment signal is present for the angular momentum. In
the Tweb only the most massive halos $>10^{12}$\hMsun are
perpendicular with respect to $\hat{e}_3$ (anti-aligned to filaments),
while for the Vweb the massive halos are aligned with $\hat{e}_2$,
lying along sheets. These results broadly agree with the
published literature. Nevertheless, in some publications
\citep{AragonCalvo2007,Hahn2007,AragonCalvo2014} there is an alignment signal
reported at lower halo masses $<10^{12}$\hMsun that we do not detect
in our measurements.  One possible explanation for this discrepancy
can be appreciated by carefully looking at the results for different
resolutions.  The $512^3$ grid does show a small anti-alignment for low
mass haloes indicating that this signal could be related to scales
smaller than $1$h$^{-1}$Mpc.  This would be consistent with
\citep{Paz2008} where, using a different technique, they find an
alignment for low mass haloes with the structure on small scales, and
an anti-alighment at large scales (the 2-halo term). The diversity of
results could be then interpreted as a high sensitivity of the
alignment signal to the small scale cosmic web description, including
numerical choices as to how the relevant fields are interpolated.

>>>>

There is a long observational tradition studying galactic properties
as a function of their large scale environment
\citep[e.g.][]{Oemler1974,Dressler1980,Pimbblet2002,Gomez2003,Kauffmann2004,Abbas2006,Baldry2006,Park2007,OMill2008,Gonzalez2009,Padilla2010,Wilman2010,Muldrew2012}. In
these situations the environment definition is usually based on
quantities easily accessible to observations such as local number
density or nearest neighbour measurements. With
the advent of large surveys the visibility of the cosmic web became
clear. As a consequence, in order to capture its filamentarity, the
environment definition started to be more complex, involving shear and gradient properties of the galaxy density field or the reconstructed dark
matter density/velocity field
\citep[e.g.][]{Lee2005,AragonCalvo2007,Hahn2007,Sousbie2008,Zhang2009,Tweb,MunozCuartas2011,Vweb,Trowland2013,Tempel2014},
including recent developments that take into account the rotational
part of the velocity field \citep[e.g.][]{Wang2013,LibeskindVorticity}.

@@

We caution the reader that the results reported by
\citep{Vweb, Libeskind2013} use a velocity field that is
calculated by a gaussian smoothing of the CIC velocity field without
taking into account any weight by mass.

@@

A much weaker alignment signal is present for the angular momentum. In
the Tweb only the most massive halos $>10^{12}$\hMsun are
perpendicular with respect to $\hat{e}_3$ (anti-aligned to filaments),
while for the Vweb the massive halos are aligned with $\hat{e}_2$,
lying along sheets. These results broadly agree with the
published literature. Nevertheless, in some publications
\citep{AragonCalvo2007,Hahn2007,AragonCalvo2014} there is an alignment signal
reported at lower halo masses $<10^{12}$\hMsun that we do not detect
in our measurements. Actually \cite{AragonCalvo2014} confirms the mass
$10^{12}$\hMsun as a transitional scale between alignment
/anti-alignment in filaments, showing that it reflects the degree of
evolution of the host filament.

One possible explanation for this discrepancy
can be appreciated by carefully looking at the results for different
resolutions.  The $512^3$ grid does show a small anti-alignment for low
mass haloes indicating that this signal could be related to scales
smaller than $1$h$^{-1}$Mpc.  This would be consistent with
\citep{Paz2008} where, using a different technique, they find an
alignment for low mass haloes with the structure on small scales, and
an anti-alighment at large scales (the 2-halo term). The diversity of
results could be then interpreted as a high sensitivity of the
alignment signal to the small scale cosmic web description, including
numerical choices as to how the relevant fields are interpolated.
